TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-08-13 paper/draft.tex
gaia acknowledgements

\shorttitle{Birky et al.}
\shortauthors{Birky et al.}

@@

\color{gcolor}{JB: Gaia acknowledgment}\color{black}

>>>>

\shorttitle{temperatures and metallicities for m dwarfs}
\shortauthors{birky et al.}

@@

This work has made use of data from the European Space Agency (ESA) mission
{\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement.
